### 2016-03-10 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Improve guideline 2.x
Update figure: exp. fitting

\researchBasedOn[This section]{Lumori2014TIM}

@@

The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others.
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
This capability is very useful for model validation and/or selection \citep{Pintelon2012}.

@@

The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak}
   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak}
   \includegraphics{\thisDir/figs/LPMfigOmegak}
   \caption{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained. This procedure is repeated for all $\Omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_\text{poly}(\Omega_k)$.

@@

\begin{align}
\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}

@@

\begin{enumerate}
\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{se:DCvalueEst}. Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$. %In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:

\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per Assumption \ref{ass:decay90perctime}.

@@

\begin{figure}[tbh] %top bottom here
\centering

\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
\caption{Truncation of the impulse response via the fit of  an exponential. The light gray line is the noisy impulse response, and the dark gray one is its absolute value. Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. Black thick line: estimated exponential function \eqref{eq:expFit}.}
\label{FRF_truncate_expfitter}
\end{figure}

@@

\item
The bias error is highest in the vicinity of (sharp) resonance peaks. If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used. %If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.

@@

\begin{figure}[tbh] %top bottom here
\centering

\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}

\caption{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$. The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc). Dots: \gls{FRF} estimates $\hat{G}$. Crosses: sample standard deviations $\hat{\sigma}$. Dashed lines: bias $\hat{b}$. White line: the true system $G_0$.}
\label{figLPMvsTrunc}
\end{figure}

@@

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering

	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
 \caption{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}). Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}

   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}

>>>>

\researchBasedOn[This section]{Lumori2014TIM}
\TODO{figures to TikZ}
\TODO{re-introduce $F$-test truncator and box-carr averager}

@@

The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.

@@

The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak}
   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak}
   \includegraphics{\thisDir/figs/LPMfigOmegak}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained. This procedure is repeated for all $\Omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_\text{poly}(\Omega_k)$.

@@

\begin{align}
\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}

@@

\begin{enumerate}
\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{se:DCvalueEst}. 
Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per Assumption \ref{ass:decay90perctime}.

@@

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
% \includegraphics[scale=0.9]{\thisDir/figs/expFitest}
\input{\thisDir/figs/expfit.tikz}
\caption{Truncation of the impulse response via the fit of  an exponential. The light gray line is the noisy impulse response, and the dark gray one is its absolute value. Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. Black thick line: estimated exponential function \eqref{eq:expFit}.}
\label{FRF_truncate_expfitter}
\end{figure}

@@

\item The bias error is highest in the vicinity of (sharp) resonance peaks. 
If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.

@@

\begin{figure}[tbh] %top bottom here
    \centering
    \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
    \caption{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$. The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc). Dots: \gls{FRF} estimates $\hat{G}$. Crosses: sample standard deviations $\hat{\sigma}$. Dashed lines: bias $\hat{b}$. White line: the true system $G_0$.}
    \label{figLPMvsTrunc}
\end{figure}

@@

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
         \caption{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}). Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}
